Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-02 draft.tex
first steps toward revising section 4

The universal property of centralizer (definition~\ref{D:centralizer}) implies that, for any $E_n$-algebras maps $A\stackrel{f}\to B$ and
$B\stackrel{g}\to C$, there are natural morphisms
\begin{equation}\label{eqdef:canonicaltocentralizers} {\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f)
\end{equation}

in the $\infty$-catgeory of $E_n$-algebras which are given by the  
following commutative diagrams of $E_n$-algebras:
\[\begin{tikzcd}
&   {\frak Z}_{E_n}(g) \otimes  {\frak Z}_{E_n}(f) \otimes A \arrow[rr, "\id\otimes \ev_f"] &&  {\frak Z}_{E_n}(g) \otimes  B \arrow[dr, "\ev_g"]\\
A \arrow[ur, "1\otimes \id_A"] \arrow[rr, "f"] && B \arrow[rr, "g"] \arrow[ur, "1\otimes \id_B"] && C. 
\end{tikzcd}\]
 When $f=g=\id_A:A\to A$, we obtain a canonical morphism \begin{equation} \label{eq:dgAssofcenter}
 {\frak Z}_{E_n}(A){\otimes} {\frak Z}_{E_n}(A) \longrightarrow {\frak Z}_{E_n}(A).\end{equation}
 Lurie has proved that this multiplication makes the center into an (homotopy) dg-associative algebras in $E_n$-algebras 
 and therefore an $E_{n+1}$-algebra. Precisely: 
\begin{prp}[\cite{LurieHA} Section 5] \label{P:PtyCenter}
\begin{itemize}
 \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_{E_n}(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
 $E_n$-algebras.
 \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(E_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
\end{itemize}
\end{prp}
When $A$ is a factorization algebra model for $A$, in virtue of theorem~\ref{T:En=Fac} 
(and \greg{add reference for fac algebra in fac algebra maybe too}), in order to have a factorization algebra 
model of the center of $A$, it is sufficient to describe the induced map 
\[{\frak Z}(A){\otimes} {\frak Z}(A) \longrightarrow {\frak Z}(A)\]
as a factorization algebra homomorphism which makes it an associative object in the category of locally constant factorization algebras.

@@

\begin{lmm}\label{L:NatPptyofComp}
 The following diagram of factorization algebras 
 \[\tiny \begin{tikzcd}
 \clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
 \otimes  \clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big) 
 \otimes \cliels(\fg \otimes \Omega_c  \big) \arrow[rd, "(-\star-)\otimes \id"]
 \arrow[dd, "\id\otimes \ev_ {\mathbf{f}}"]& \\ 
 & \clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
 \otimes \cliels(\fg \otimes \Omega_c  \big)
 \arrow[dd, "\ev_{\mathbf{g}\circ \mathbf{f}}"]\\
\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
 \otimes \cliels(\fh \otimes \Omega_c  \big)  \arrow[rd, "\ev_{\mathbf{g}}"] & \\  & \cliels(\fl \otimes \Omega_c  \big). 
\end{tikzcd}\]
 is commutative.
\end{lmm}
\begin{proof}

\begin{thm}\label{T:compcentralizer}
 Let $f: \fg \to \fh$, $g: \fh \to \fl$ be  $L_\infty$-algebras morphisms.
\begin{enumerate} \item 
 The composition $(-\star-)$ of factorization algebras (definition~\ref{def:comp}) 
 is the canonical map 
\[{\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f).\] 
\item If $f= \fg \stackrel{\id}\to \fg$,  the composition $(-\star-)$ makes 
$\clies\big(\fg \otimes \Omega, \cliels(\fg \otimes \Omega_c) \big)$ into an 
(augmented) associative algebra object in factorization algebra, with unit given by $\mathbf{1}$, 
which is equivalent to the structure of the center ${\frak Z} (\cliels(\fg \otimes \Omega_c))$. 
\end{enumerate}
\end{thm}
\begin{proof}
By universal property of centralizers, the canonical map~\eqref{eqdef:canonicaltocentralizers}  
is the unique\footnote{it is unique in the $\infty$-categorical 
sense, that is there is a contractible space of choices for it} map 
\[ \Upsilon: {\frak Z}_{E_n}(\UU_n g) \otimes {\frak Z}_{E_n}(\UU_n f) \longrightarrow {\frak Z}_{E_n}\big(\UU_n (g\circ f)\big)\] 
of $E_n$-algebras which makes the following diagram
\begin{equation}\label{eq:comdiagforcentralizercomput}\small
 \xymatrix{
&   &&  
{\frak Z}_{E_n}\big(\UU_n (g\circ f) \big) \otimes  \UU_n \fg  \ar@/^{2pc}/[dddr]^{\ev_{\UU_n (g\circ f)}}\\
&{\frak Z}_{E_n}(\UU_n g) \otimes  {\frak Z}_{E_n}(\UU_n f) \otimes \UU_n \fg \ar@/^{1pc}/[rru]_{ \Upsilon \otimes \id_{\UU_n \fg}} \ar[rrd]_{\id\otimes \ev_{\UU_n f}}
&& (1)
& & \\
\UU_n \fg \ar[ur]_{1^{\otimes 2}\otimes \id_{\UU_n \fg}} \ar@/_{1pc}/[rrd]^{\UU_n f} \ar@/^{6pc}/[rrruu]_{1\otimes \id_{\UU_n \fg}} &&&
{\frak Z}_{E_n}(\UU_n g) \otimes \UU_n \fh \ar[rd]^{\ev_{\UU_n h}}  &\\
&& \UU_n \fh \ar[rr]^{\UU_n g} \ar[ur]^{1\otimes \id_{\UU_n \fh}} && \UU_n \fl .}
\end{equation}
commutative (since $\UU_n (g\circ f) = \UU_n g\, \circ \, \UU_n f $;  the commutativity of the lower part of the diagram being by definition of centralizers).

>>>>

The universal property of centralizer (recall definition~\ref{D:centralizer}) implies that 
for any maps $A\stackrel{f}\to B$ and $B\stackrel{g}\to C$ of $E_n$-algebras, 
there is a natural morphism
\begin{equation}
\label{eqdef:canonicaltocentralizers} 
{\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f)
\end{equation}
in the $\infty$-category of $E_n$-algebras that arises from  
following commutative diagram of $E_n$-algebras:
\[
\begin{tikzcd}
&   {\frak Z}_{E_n}(g) \otimes  {\frak Z}_{E_n}(f) \otimes A \arrow[rr, "\id\otimes \ev_f"] &&  {\frak Z}_{E_n}(g) \otimes  B \arrow[dr, "\ev_g"]\\
A \arrow[ur, "1\otimes \id_A"] \arrow[rr, "f"] && B \arrow[rr, "g"] \arrow[ur, "1\otimes \id_B"] && C. 
\end{tikzcd}
\]
When $f=g=\id_A:A\to A$, we thus obtain a canonical morphism 
\begin{equation} 
\label{eq:dgAssofcenter}
{\frak Z}_{E_n}(A){\otimes} {\frak Z}_{E_n}(A) \longrightarrow {\frak Z}_{E_n}(A).
\end{equation}
Lurie \cite{HA} has proved that this multiplication makes the center into an $E_1$ algebra in $E_n$-algebras 
and therefore an $E_{n+1}$-algebra, by Dunn additivity. 
%To be precise, there is the following result.
%
%\begin{prp}[\cite{LurieHA} Section 5] 
%\label{P:PtyCenter}
%\begin{itemize}
% \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_{E_n}(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
% $E_n$-algebras.
% \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(E_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
%\end{itemize}
%\end{prp}

A compelling aspect of our construction is that it lets one see these properties in a barehanded fashion,
using familiar formulas with $L_\infty$ algebras.
(More accurately, via composition of convolution algebras.)
The goal of this section is to prove directly the following result.

\owen{I'm pooping out, but it should be straightforward to revise this in light of our revisions above.}

\begin{thm}
\label{T:compcentralizer}
 Let $f: \fg \to \fh$ and $g: \fh \to \fl$ be maps of  $L_\infty$-algebras.
\begin{enumerate} 
\item The composition $(-\star-)$ of factorization algebras (definition~\ref{def:comp}) is the canonical map 
\[{\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f).\] 
\item If $f= \fg \stackrel{\id}\to \fg$,  the composition $(-\star-)$ makes 
$\clies\big(\fg \otimes \Omega, \cliels(\fg \otimes \Omega_c) \big)$ into an 
(augmented) associative algebra object in factorization algebra, with unit given by $\mathbf{1}$, 
which is equivalent to the structure of the center ${\frak Z} (\cliels(\fg \otimes \Omega_c))$. 
\end{enumerate}
\end{thm}

When $A$ is a factorization algebra model for $A$, in virtue of theorem~\ref{T:En=Fac} 
(and \greg{add reference for fac algebra in fac algebra maybe too}), in order to have a factorization algebra 
model of the center of $A$, it is sufficient to describe the induced map 
\[{\frak Z}(A){\otimes} {\frak Z}(A) \longrightarrow {\frak Z}(A)\]
as a factorization algebra homomorphism which makes it an associative object in the category of locally constant factorization algebras.

@@

\begin{lmm}\label{L:NatPptyofComp}
 The following diagram of factorization algebras 
 \[\tiny \begin{tikzcd}
 \clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
 \otimes  \clies\big(\fg \otimes \Omega, \cliels(\fh \otimes \Omega_c  \big) 
 \otimes \cliels(\fg \otimes \Omega_c  \big) \arrow[rd, "(-\star-)\otimes \id"]
 \arrow[dd, "\id\otimes \ev_ {\mathbf{f}}"]& \\ 
 & \clies\big(\fg \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
 \otimes \cliels(\fg \otimes \Omega_c  \big)
 \arrow[dd, "\ev_{\mathbf{g}\circ \mathbf{f}}"]\\
\clies\big(\fh \otimes \Omega, \cliels(\fl \otimes \Omega_c  \big) 
 \otimes \cliels(\fh \otimes \Omega_c  \big)  \arrow[rd, "\ev_{\mathbf{g}}"] & \\  & \cliels(\fl \otimes \Omega_c  \big). 
\end{tikzcd}\]
 is commutative.
\end{lmm}

\begin{proof}
\end{proof}

\begin{proof}[Proof of Theorem~\ref{T:compcentralizer}]
By universal property of centralizers, the canonical map~\eqref{eqdef:canonicaltocentralizers}  
is the unique\footnote{it is unique in the $\infty$-categorical 
sense, that is there is a contractible space of choices for it} map 
\[ \Upsilon: {\frak Z}_{E_n}(\UU_n g) \otimes {\frak Z}_{E_n}(\UU_n f) \longrightarrow {\frak Z}_{E_n}\big(\UU_n (g\circ f)\big)\] 
of $E_n$-algebras which makes the following diagram
\begin{equation}\label{eq:comdiagforcentralizercomput}\small
 \xymatrix{
&   &&  
{\frak Z}_{E_n}\big(\UU_n (g\circ f) \big) \otimes  \UU_n \fg  \ar@/^{2pc}/[dddr]^{\ev_{\UU_n (g\circ f)}}\\
&{\frak Z}_{E_n}(\UU_n g) \otimes  {\frak Z}_{E_n}(\UU_n f) \otimes \UU_n \fg \ar@/^{1pc}/[rru]_{ \Upsilon \otimes \id_{\UU_n \fg}} \ar[rrd]_{\id\otimes \ev_{\UU_n f}}
&& (1)
& & \\
\UU_n \fg \ar[ur]_{1^{\otimes 2}\otimes \id_{\UU_n \fg}} \ar@/_{1pc}/[rrd]^{\UU_n f} \ar@/^{6pc}/[rrruu]_{1\otimes \id_{\UU_n \fg}} &&&
{\frak Z}_{E_n}(\UU_n g) \otimes \UU_n \fh \ar[rd]^{\ev_{\UU_n h}}  &\\
&& \UU_n \fh \ar[rr]^{\UU_n g} \ar[ur]^{1\otimes \id_{\UU_n \fh}} && \UU_n \fl .}
\end{equation}
commutative (since $\UU_n (g\circ f) = \UU_n g\, \circ \, \UU_n f $;  the commutativity of the lower part of the diagram being by definition of centralizers).
